### 2022-05-18 manuscript.Rmd
Proof reading by A.E.

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

    # Recode mean sample age in years (mean-centered) for meta-regression
    age = age_mean / 365.25,
    age_c = age - mean(age, na.rm = TRUE),
    age_sd = age_sd / 365.25,

@@

@@

Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months. We robustly found that male infants recognized novel rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

@@

Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013]. Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$). Interestingly, a recent meta-analysis [@lauer2019a] in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted $g = 0.39$). Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.

In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018]. All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985]. These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]). In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object. Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation. In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle. Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle. Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown. Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle. In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.

@@

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

@@

@@

(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants. White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals. Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI). These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)). The probability for this effect being greater than zero was `r print_perc(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, approximately `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

@@

To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level. This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

    # Plot the funnels
    ggplot(dat, aes(x = gi, y = sei)) +
      # Funnels under the null hypothesis
      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
      scale_fill_manual(
        values = c("gray80", "grey90", "white"),
        breaks = c("greater_05", "smaller_05", "smaller_01"),
        labels = c(
          expression(italic(p) > .05),
          expression(italic(p) < .05),
          expression(italic(p) < .01)
        )
      ) +
      # Grid lines
      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
      # Observed_funnel
      geom_path(data = funnel_observed, aes(x = x, y = y)) +
      # Meta-analytic effect size
      geom_vline(xintercept = summ$intercept, color = "black") +
      # Experiment-specific effect sizes
      geom_point(shape = 0) +
      # Styling
      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
      scale_y_reverse() +
      coord_cartesian(
        xlim = c(-2.5, 2.5),
        ylim = c(max_se, 0),
        expand = FALSE
      ) +
      labs(
        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
        fill = "Significance level"
      ) +
      theme_classic() +
      theme(
        axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "Helvetica", color = "black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        text = element_text(family = "Helvetica", color = "black")
      )
  }
) -> plots_funnel

@@

(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (**a**) and for the meta-analysis of gender differences in mental rotation performance (**b**). The plots show the standard error and effect size for each of the individual experiments as a black square. The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line). Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis. These shades thus illustrate which of the original studies observed a significant effect. For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of studies with high standard errors and small effect sizes suggests a small publication bias.

@@

We analyzed looking times during mental rotation in `r formatC(descriptives$n_infants, big.mark = ",")` infants ranging from `r descriptives$min_age_months` to `r descriptives$max_age_months` months of age. To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes. We found that male infants looked on average longer at novel rotated objects compared to female infants. This effect was small and unrelated to age in the current range.

We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females. The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females. In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size. This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.

@@

Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019]. Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.

A number of additional factors have been associated with individual differences in infant mental rotation performance. For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task [@mohring2013; @schwarzer2013a; @slone2018]. This relation also applies to previous experience with manually rotating toys [@schwarzer2013a]. While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g. [@ausubel1968; @bradley1983; @halberda2008]). Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].

@@

In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021]. The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) and Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.

@@

We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression. To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)). These models were fitted using restricted maximum likelihood estimation (REML). To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.\ \@ref(fig:figs4)).

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{lineno}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

    # Recode mean sample age in years (mean-centered) for meta-regression
    age = age_mean / 365.25,
    age_c = age - mean(age, na.rm = TRUE),

@@

\linenumbers

@@

Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months. We robustly found that male infants recognized rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

@@

Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013]. Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$). Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents [@lauer2019a] suggests even only a small-to-medium difference (mean weighted $g = 0.39$). Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.

In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018]. All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985]. These experiments comprised real world stimuli (e.g., toy objects) [@antrilli2016], three-dimensional digital stimuli (e.g., cube figures) [@moore2008], or two-dimensional digital stimuli (e.g., digits) [@quinn2008]. In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object. Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation. In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle. Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle. Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown. Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle. In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.

@@

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

@@

(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants. White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals. Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI). These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the data. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

@@

For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)). The probability for this effect being greater than zero was $\approx$ `r print_perc(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

@@

To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_gender$icc)` was attributable to differences *between* articles.

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

    # Plot the funnels
    ggplot(dat, aes(x = gi, y = sei)) +
      # Funnels under the null hypothesis
      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
      scale_fill_manual(
        values = c("gray80", "grey90", "white"),
        breaks = c("greater_05", "smaller_05", "smaller_01"),
        labels = c(
          expression(italic(P) > 0.05),
          expression(italic(P) < 0.05),
          expression(italic(P) < 0.01)
        )
      ) +
      # Grid lines
      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
      # Observed_funnel
      geom_path(data = funnel_observed, aes(x = x, y = y)) +
      # Meta-analytic effect size
      geom_vline(xintercept = summ$intercept, color = "black") +
      # Experiment-specific effect sizes
      geom_point(shape = 0) +
      # Styling
      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
      scale_y_reverse() +
      coord_cartesian(
        xlim = c(-2.5, 2.5),
        ylim = c(max_se, 0),
        expand = FALSE
      ) +
      labs(
        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
        fill = "Significance level"
      ) +
      theme_classic() +
      theme(
        axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "Helvetica", color = "black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        text = element_text(family = "Helvetica", color = "black")
      )
  }
) -> plots_funnel

@@

(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (**a**) and for the meta-analysis of gender differences in mental rotation performance (**b**). The plots show the standard error and effect size for each of the individual experiments as a black square. The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line). Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis. These shades thus illustrate which of the original experiments observed a significant effect. For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of experiments with high standard errors and small effect sizes suggests a small publication bias.

@@

We analyzed looking times during mental rotation in `r formatC(descriptives$n_infants, big.mark = ",")` infants ranging from `r descriptives$min_age_months` to `r descriptives$max_age_months` months of age. To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes. We found that on average, male infants looked longer at novel rotated objects compared to female infants. This effect was small and unrelated to age in the current range.

We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females. The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely report separate effect sizes for males and females. In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size. This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.

@@

Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019]. However, possible biological developmental pathways, bridging the gap from hormonal to behavioral differences, are currently far from understood.

A number of additional factors have been associated with individual differences in infant mental rotation performance. For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task [@mohring2013; @schwarzer2013a; @slone2018]. This relation also applies to previous experience with manually rotating toys [@schwarzer2013a]. While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g. [@ausubel1968; @bradley1983; @halberda2008]). Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].

@@

In the present meta-analysis, we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021]. The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) while Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.

@@

We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression. To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)). These models were fitted using restricted maximum likelihood estimation (REML). To verify that this procedure converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Fig.\ \@ref(fig:figs4)).
